Trip Summary ITHIM-R

### 2019-10-04 code/producing_trips_rd/trip-summary.Rmd
adding trip summary table

---
title: "Summary Tables ITHIMR"
author: "Lambed Tatah, MRC Epidemiology Unit, University of Cambridge, UK"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
---

```{r, setup, comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F, include=FALSE, results='asis'}

source("J:/Group/lambed/ITHIM-R/code/producing_trips_rd/used_functions.R")

@@

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/santiago/santiago_trip.csv")
quality_check(trip)
trip_summary$santiago <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/bogota/bogota_trip.csv")
quality_check(trip)
trip_summary$bogota <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/accra/accra_trip.csv")
quality_check(trip)
trip_summary$accra <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/delhi/delhi_trip.csv")
quality_check(trip)
trip_summary$delhi <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/bangalore/bangalore_trip.csv")
quality_check(trip)
trip_summary$bangalore <- value

@@

print(kable_styling(kable(trip_summary)))

@@

>>>>

---
title: "Trip Summary ITHIM-R"
author: "Lambed Tatah, MRC Epidemiology Unit, University of Cambridge, UK"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    html_document:
        theme: null
---

```{r, include = FALSE}
source("J:/Group/lambed/ITHIM-R/code/producing_trips_rd/used_functions.R")

```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}

@@

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/santiago/santiago_trip.csv")
quality_check(trip)
trip_summary$santiago_city <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/bogota/bogota_trip.csv")
quality_check(trip)
trip_summary$bogota_city <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/accra/accra_trip.csv")
quality_check(trip)
trip_summary$accra_city <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/delhi/delhi_trip.csv")
quality_check(trip)
trip_summary$delhi_city <- value

trip <- read_csv("J:/Group/lambed/ITHIM-R/data/local/bangalore/bangalore_trip.csv")
quality_check(trip)
trip_summary$bangalore_city <- value

@@

@@

```{r, include = TRUE,  echo= FALSE, results='asis'}
kable(trip_summary) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 14, fixed_thead = T)
